Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-09-30 WSSSPE3/report/wg_main_publishing_SW.tex

This group explored the value of executable papers (papers whose content includes
the code needed to produce their own results), and other forms of publishing which
include dynamic electronic content. Transitioning to this type of publication offers
possibilities of addressing, or partially addressing sustainability concerns 
such as reproducibility (the paper contains all the artifacts needed to verify its
results), transitive credit (modules an executable paper depends on must be explicitly
loaded, making it more feasible to identify them), and improving documentation (an executable
paper must explain what its code does).

@@

Best Practices: Because an executable paper showcases the code

\subsubsection{Fit with related activities}
\todo{short text here - can include links/cites}

\subsubsection{Discussion}
\todo{short-ish text here}

\subsubsection{Plans}
\todo{short text here - not bullets}

@@

A page will be made available on the Software Sustainability Institute website.

>>>>

This group explored the value of executable papers (papers whose content includes
the code needed to produce their own results), and other forms of publishing which
include dynamic electronic content. Transitioning to this type of publication offers
possibilities of addressing, or partially addressing sustainability concerns 
such as reproducibility, transitive credit, and best practices.

\subsubsection{Fit with related activities}

@@

Best Practices: Because an executable paper showcases the code, and the code itself
is subject to the review process, authors are more likely to pay attention to coding
practices. In addition, because the paper must explain what the code does, better
documentation is likely to be achieved.

\subsubsection{Discussion}

The group felt that the best way to encourage the use of these new publishing
concepts would be to create and curate a list identifying publishing venues
that support them. The Software Sustainability Institute agreed to host this list.

\subsubsection{Plans}

The plan is to create a web page describing executable papers, their value, and
a list of what publishers support them.

@@

The afforementioned page to be published on SSI.
